Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-01-12 main.tex
Update on Overleaf.

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement code \textsc{Enzo}. For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species \textbf{list here?}. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods on a \textbf{XX Myr} simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. Our methods are capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis, with first results presented in a companion paper \textit{reference here?}.
\end{abstract}

@@

\subsubsection{Type Ia Supernova}
\label{sec:Type Ia}
We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors. \textbf{This is the most self-consistent model for Type 1a supernovae in galaxy scale simulations. (worth mentioning? maybe softer version of this?)} We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time. For example, by the end of the simulation presented here (XXX Myr), only XXX have gone off. At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
%or, 
%\[
%M_{\rm WD} = 
%\begin{cases}
%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
%\end{cases}
%\]
%where $M_{\rm *}$ is the initial mass of the WD progenitor.
We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.

@@

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8}~M_{\odot}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc. This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012} (need more cite). We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.

@@

\section{Results}
\label{sec:results}
We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first \textbf{350 Myr} after the first star forms. This occurs 43 Myr after initialization. Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.\footnote{All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.}

Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle formed, and the galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation \textit{(list times here)}. In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is \textbf{$389 \pm 21$ pc}, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

@@

The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}. This figure shows the 30~Myr time averaged scale height of all gas in the disk throughout the simulated time. Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights between 50--200~pc. Although the disk remains thin beyond the stellar radius of our galaxy, it is resolved at all radii. The low central scale heights at 100 Myr (dashed, purple) compared to those at 200-300~pc are due to a general lack of gas in this central region from the initial burst of star formation. This is clear in the density panels of Fig~\ref{fig:panel_x}. Although the cold disk is thin, this property is currently unconstrained in galaxies of this mass due to low ($\sim$ 100 pc or worse) spatial resolution \citep[e.g.][]{Bernstein-Cooper2014}.
%We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here). $H$ is generally larger than the scale height by a factor of 2, but is comparable to the scale height at radii with ongoing star formation, indicating a particularly uniform-then-truncated density distribution. At large radii, away from active star formation, $H$ is roughly 50 pc, or $\sim$ 3 times the scale height.

@@

We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}. (By the end of the simulation, there have \textbf{only been XX Type 1a supernovae}.) Within the first 40 Myr of evolution the SFR rises quickly to between $2--4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ for the remainder of the simulation, with large fluctuations. The SNR tracks the SFR with a time delay, capturing the rough rule of thumb that there is one core collapse supernovae per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.33 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$. We note the discontinuity in SFR near 340~Myr represents a 10~Myr period without any star formation. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction doubles over time to roughly 35\%. This is because the total amount of mass in the disk decreases through feedback driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snr}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time. Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM). We emphasize that the molecular ISM phase is defined as all regions with f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas. See Appendix \ref{appendix:phases} for a quantitative definition of these phases. Each of these exist in our simulations, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and diffuse and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the phase properties of the gas within the inner halo of our dwarf galaxy.

Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the final 50 Myr of simulation time. One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}). Several notable features of the phase diagram include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average. We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work. \textbf{is last bit on CR heating and SF gas OK?}

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over the final 50 Myr of simulation time. The two red dashed lines show lines of constant pressure for guidance. The region in the lower right corner indicates our density and temperature thresholds for star formation.}
\label{fig:phase}
\end{figure}

The mass of the ISM in our dwarf galaxy is dominated by the CNM over the entire simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. Together, the CNM and WNM comprise roughly 90\% of the galaxy's mass throughout most of its evolution. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume each, though the two warm phases dominate. The volume fractions are subject to significantly more fluctuations over time, due to the low SFR and supernova rate of our galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. These results are in some contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. \textbf{Note to look into this / discuss a little further since it is different than previous sims}

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. This figure only includes gas present within the disk of the galaxy.}
\label{fig:ISM_evolution}
\end{figure*}

@@

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The contribution from the metagalactic background falls below the lower vertical axis limit on this plot. Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars. However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.

\textbf{Note to remember to discuss: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e. how does this compare to a uniform or 1D radial profile). G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret. Though possibly I should show both?}

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over the final 50 Myr of simulation time. Here we define the midplace as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the \ion{H}{1} ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values only. \ion{He}{1} is very similar to \ion{H}{1}, with a small vertical offset, and is not shown for clarity.}
\label{fig:ISRF}
\end{figure}

@@

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}. We use the 10 Myr averaged SFR to compute the mass loading rates. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time. This quickly declines towards larger radii, however, with minimal outflow past the virial radius. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift. Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.

@@

\subsection{Metal Evolution} 
\label{sec:chemical evolution}
\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper.}

>>>>

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement code \textsc{Enzo}. For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species \textbf{list here?}. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods on a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. Our methods are capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis.
\end{abstract}

@@

\subsubsection{Type Ia Supernova}
\label{sec:Type Ia}
We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors. This is the most self-consistent model for Type 1a supernovae in galaxy scale simulations. \textbf{(Is this worth mentioning like this? or too strong a statement?)} We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time. For example, by the end of the simulation presented here (500~Myr), only 18 have gone off. At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
%or, 
%\[
%M_{\rm WD} = 
%\begin{cases}
%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
%\end{cases}
%\]
%where $M_{\rm *}$ is the initial mass of the WD progenitor.
We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.

@@

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8}~M_{\odot}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc. This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012}. We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.

@@

\section{Results}
\label{sec:results}
We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms. This occurs 43 Myr after initialization. Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle formed, and the galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy.

Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}. All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation \textit{(list times here)}. In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

@@

The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}. This figure shows the 40~Myr time averaged scale height of all gas in the disk centered on the given time. Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights between 50--200~pc. Although the disk remains thin beyond the stellar radius of our galaxy (a scale height of around 40~--~60~pc), it is resolved at all radii. By the end of the simulation, the majority of the gas has a scale height of $\sim$100~pc. Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging. For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100 - 200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
%We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here). $H$ is generally larger than the scale height by a factor of 2, but is comparable to the scale height at radii with ongoing star formation, indicating a particularly uniform-then-truncated density distribution. At large radii, away from active star formation, $H$ is roughly 50 pc, or $\sim$ 3 times the scale height.

@@

We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type 1a rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between $2--4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations. By the end of the simulation, the SFR is very low and infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$. The SNR tracks the SFR with a time delay, with roughly one core collapse supernovae per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\% and is about equal with the HI gas. This is because the total amount of mass in the disk decreases through feedback driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snr}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time. Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM). We emphasize that the molecular ISM phase is defined as all regions with f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas. See Appendix \ref{appendix:phases} for a quantitative definition of these phases. Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and diffuse and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the phase properties of the gas within the inner halo of our dwarf galaxy.

Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300 -- 350~Myr. One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}). Several notable features of the phase diagram include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average. We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work. \textbf{is last bit on CR heating and SF gas OK?}

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr. The two red dashed lines show lines of constant pressure for guidance. The region in the lower right corner indicates our density and temperature thresholds for star formation.}
% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
\label{fig:phase}
\end{figure}

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. At this point the molecular component dominates through the end of the simulation.

Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. \textbf{Do I need to discuss a little further since it is different than previous sims? If so, where should I go with this?}

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM.}
% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
\label{fig:ISM_evolution}
\end{figure*}

@@

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 50 Myr from 300--350~Myr. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The contribution from the metagalactic background falls below the lower vertical axis limit on this plot. Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars. However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.

\textbf{In response to MM's comment: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e. how does this compare to a uniform or 1D radial profile). G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret. Though possibly I should show both?}

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the \ion{H}{1} ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values only. \ion{He}{1} is very similar to \ion{H}{1}, with a small vertical offset, and is not shown for clarity.}
\label{fig:ISRF}
\end{figure}

@@

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}. Generally, other works use long timescale measurements of the SFR ($\sim$~Gyr) to compute the mass loading factor. For consistency in these works, we use the 500~Myr average SFR for computing the mass loading factor. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time. This quickly declines towards larger radii, however, with minimal outflow past the virial radius. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift. Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.

@@

\subsection{Metal Evolution} 
\label{sec:chemical evolution}
\textbf{This section saw significant change. Removed previous mention of stellar abundances and species retention fractions. Much of below is new(ish)}
